ML Estimation of Matrix--$t$ Distributions with Expectation Maximization

### 2017-02-02 paper.tex
Mention the joint density somewhere
This is used in the next section but not mentioned explicitly
anywhere.

From the definitions in Eqs.~\eqref{eq:tdef1} and \eqref{eq:tdef2},
and the densities given above, it follows that the density function
$f(T;\left\{M,\Sigma,\Omega,\nu\right\})$ of a matrix--$t$
distribution $T_{p,m}(M,\Sigma,\Omega,\nu)$ satisfies
\begin{equation}
\frac{\Gamma_{p}\left(\frac{p+\nu+m-1}{2}\right)}%
{\Gamma_{p}\left(\frac{\nu+p-1}{2}\right)%
\pi^{\frac{mp}{2}}|\Omega|^{\frac{p}{2}}|\Sigma|^{\frac{m}{2}}}%
|I_p+\Sigma^{-1}(T-M)\Omega^{-1}(T-M)^{\textrm{t}}|^{\frac{1-m-p-\nu}{2}}
\label{eq:matrixtpdf}
\end{equation}
%
with $I_p$ the identity matrix of dimension $p$. The marginalization
over $S$ can be obtained by using the Jacobain determinant of an
inverse SPD matrix $U=S^{-1}$
%
\begin{equation}
\left|\frac{\partial U}{\partial S}\right|=|S|^{-p-1}
\end{equation}
and the integral identity \citep{gupta1999matrix}
\begin{equation}
\int_{\mathbf{S}_{++}^p}e^{-\textrm{tr}[S A]}|S|^{\alpha}\,dS=%
\Gamma_{p}\left(\alpha+\frac{1+p}{2}\right)|A|^{-\alpha-\frac{1+p}{2}}
\ .\label{eq:intmultgammadef}
\end{equation}
Where $A$ is a $p\times p$ nonsingular matrix.

>>>>

The density of the matrix--$t$ distribution can be obtained by
computing the joint density of $S$ and $T$ taken as independent
variables $f\left(T,S; (M,\Sigma,\Omega,\nu)\right)$, as the product
of the matrix normal and inverse Wishart densities
Eqs.~\eqref{eq:ndistpdf} and \eqref{eq:wdistpdf}, and then integrating
the hidden parameter $S$  over the field of SPD matrices, as follows
from the definitions in Eqs.~\eqref{eq:tdef1} and \eqref{eq:tdef2}.

The density function
$f(T;\left\{M,\Sigma,\Omega,\nu\right\})$ of a matrix--$t$
distribution $T_{p,m}(M,\Sigma,\Omega,\nu)$ satisfies
\begin{equation}
\frac{\Gamma_{p}\left(\frac{p+\nu+m-1}{2}\right)}%
{\Gamma_{p}\left(\frac{\nu+p-1}{2}\right)%
\pi^{\frac{mp}{2}}|\Omega|^{\frac{p}{2}}|\Sigma|^{\frac{m}{2}}}%
|I_p+\Sigma^{-1}(T-M)\Omega^{-1}(T-M)^{\textrm{t}}|^{\frac{1-m-p-\nu}{2}}
\label{eq:matrixtpdf}
\end{equation}
%
with $I_p$ the identity matrix of dimension $p$.

The marginalization
over $S$ can be obtained by using the Jacobain determinant of an
inverse SPD matrix $U=S^{-1}$
%
\begin{equation}
\left|\frac{\partial U}{\partial S}\right|=|S|^{-p-1}
\end{equation}
and the integral identity \citep{gupta1999matrix}
\begin{equation}
\int_{\mathbf{S}_{++}^p}e^{-\textrm{tr}[S A]}|S|^{\alpha}\,dS=%
\Gamma_{p}\left(\alpha+\frac{1+p}{2}\right)|A|^{-\alpha-\frac{1+p}{2}}
\ .\label{eq:intmultgammadef}
\end{equation}
Where $A$ is a $p\times p$ nonsingular matrix. The result in
eq.~\eqref{eq:matrixtpdf} then follows by direct substitution.
